\documentclass[11pt,]{article}
\usepackage[sc, osf]{mathpazo}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=.7in]{geometry}




\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% Now begins the stuff that I added.
% ----------------------------------

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\bfseries\Large}
\subsectionfont{\rmfamily\mdseries\normalsize\itshape}

\usepackage[usenames, dvipsnames]{color}
\definecolor{mygray}{gray}{0.6}

\usepackage[explicit]{titlesec}% http://ctan.org/pkg/titlesec
\def\Vhrulefill{\leavevmode\leaders\hrule height 0.0ex depth \dimexpr 0.3pt-0.0ex\hfill\kern0pt} %change both #.#ex to change height
\titleformat{\section}{\bfseries\Large}{}{0pt}{#1~\color{mygray}\Vhrulefill}
%\titleformat{\section}{\bfseries\Large}{}{0pt}{\noindent\Vhrulefill~#1~\Vhrulefill}

% Make lists without bullets
%\renewenvironment{itemize}{
%  \begin{list}{}{
%    \setlength{\leftmargin}{1.5em}
%  }
%}{
%  \end{list}
%}


% Make parskips rather than indent with lists.
\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{4pt plus 2pt minus 2pt}

% Use fontawesome. Note: you'll need TeXLive 2015. Update.
\usepackage{fontawesome}

% Fancyhdr, as I tend to do with these personal documents.
\usepackage{fancyhdr,lastpage}
\pagestyle{fancy}
\renewcommand{\headrulewidth}{0.0pt}
\renewcommand{\footrulewidth}{0.0pt}
\lhead{}
\chead{}
\rhead{}
%\lfoot{
%\cfoot{\scriptsize  Mike Konczal - Resume -  }}
%\rfoot{\scriptsize \thepage/{\hypersetup{linkcolor=black}\pageref{LastPage}}}

% Always load hyperref last.
\usepackage{hyperref}
\PassOptionsToPackage{usenames,dvipsnames}{color} % color is loaded by hyperref

\hypersetup{unicode=true,
            pdftitle={Mike Konczal:  Resume (Curriculum Vitae)},
            pdfauthor={Mike Konczal},
            pdfkeywords={R Markdown, academic CV, template},
            colorlinks=true,
            linkcolor=Maroon,
            citecolor=Blue,
            urlcolor=blue,
            breaklinks=true, bookmarks=true}
\urlstyle{same}  % don't use monospace font for urls

\begin{document}


\centerline{\huge \bf Mike Konczal}

\vspace{2 mm}

\hrule

\vspace{2 mm}
%job title

%address

\moveleft.5\hoffset\centerline{ 
%email
\faEnvelopeO \hspace{1 mm} \href{mailto:}{\color{black} \href{mailto:konczal@gmail.com}{\nolinkurl{konczal@gmail.com}}} \hspace{1 mm}
%website
\faGlobe \hspace{1 mm} \href{http://www.mikekonczal.com}{\tt www.mikekonczal.com} \hspace{1 mm}
%github
\faGithub \hspace{1 mm} \href{http://github.com/mtkonczal}{\color{black} mtkonczal} \hspace{1 mm}   
%twitter
\faTwitter \hspace{1 mm} \href{http://twitter.com/mtkonczal}{\color{black} mtkonczal} \hspace{1 mm}   
%address
\faMapPin \hspace{1 mm} \color{black} Takoma Park, MD \hspace{1 mm}   
%phone
 
 
}


\vspace{2 mm}

\hrule


\pagenumbering{arabic}

\section{Professional Summary}\label{professional-summary}

Accomplished researcher, writer, and advocate skilled in economic data
and policy analysis. I have been cited in over 300 press articles,
testified before Congress four times, and made over 50 media appearances
on platforms like \emph{CBS Sunday Morning} and \emph{Washington
Journal}. My written work has been featured in esteemed publications
such as \emph{The New York Times} and \emph{The Washington Post}.

\section{Experience}\label{experience}

\textbf{Chief Economist and Special Assistant to the President for
Economic Policy,} White House National Economic Council, Washington DC
\hfill 2024

\begin{itemize}
\item
  Provided ongoing economic analysis for the National Economic Advisor
  and support for NEC Deputy Director for fiscal and macroeconomic
  policy, including on inflation, growth, employment, tax, budget, and
  housing policy.
\item
  Developed strategic arguments for the President's economic policy
  agenda, in close consultation with colleagues at the Treasury
  Department and the Council of Economic Advisers.
\item
  Led the formulation of the White House's messaging following all
  macroeconomic data releases, including themes, statements, charts, and
  talking points. Tracked the process for data releases, created
  internal NEC measures, and directed rapid analyses and responses on
  indicators.
\item
  Amplified the economic messaging of the White House and National
  Economic Advisor, via speechwriting, content development, and media
  interaction. Regularly engaged external economic validators, experts,
  reporters, and academics on economic data as well as the President's
  agenda.
\item
  Favorably adjudicated Tier 5 investigation; Top Secret/Sensitive
  Compartmented Information (TS/SCI) clearance granted.
\end{itemize}

\textbf{Director,} Roosevelt Institute, New York, NY \hfill 2010 - 2023

\begin{itemize}
\item
  Directed the macroeconomic research team, providing original research
  on key economic issues, including inflation, growth, and employment,
  at a leading think tank. Served as a go-to expert on economic and
  policy issues for journalists and policymakers.
\item
  Authored over 20 white papers and edited four comprehensive report
  volumes. Automated real-time data analysis with R and Python across
  major data releases. Collaborated with the communications team to
  devise engagement strategies for our projects, and government
  relations to work with elected officials and other policymakers.
\item
  Orchestrated four multi-year research and policy initiatives as an
  expert on topics including the Dodd-Frank Act, the Great Recession,
  economic inequality, and evolving economic paradigms. Managed teams of
  two internal researchers and three external fellows.
\item
  Successfully secured and managed research grants from organizations
  such as the Kauffman, Ford, and Hewlett Foundations, as well as Open
  Philanthropy.
\end{itemize}

\textbf{Financial Engineer,} Moody's KMV, San Francisco, CA\hfill 2007 -
2009

\begin{itemize}
\item
  Developed testing benchmarks for Moody's KMV credit risk model,
  recognized as the 2006 ``Top Provider in Trading and Banking'' by Risk
  Magazine. Collaborated on five system releases of RiskFrontier
  software, developing test cases and acceptance criteria for
  cutting-edge credit risk modeling algorithms.
\item
  Actively participated in discussions on various approaches to credit
  risk modeling, focusing on the Vasicek-Kealhofer (VK) model derived
  from the Black-Scholes-Merton framework. Contributed to debates on
  capital requirements and loss reserving.
\item
  Prototyped research algorithms using R, SAS, Matlab, and Excel VB to
  replicate results. Designed and implemented a system that automated
  the collection, storage, and analysis of significant data sets across
  four releases, reducing test execution time by 40 percent.
\end{itemize}

\textbf{Senior Test Engineer,} Motorola, Schaumburg, IL \hfill 2001-2005

\begin{itemize}
\tightlist
\item
  Directed performance, load, and stress testing across four major iDEN
  system releases, earning a Motorola BRAVO Award for ``above and beyond
  performance contribution.'' Designed automated Six Sigma-level test
  cases using Perl, Python, and MySQL based on models of consumer
  behavior. Trained six employees in testing methods.
\end{itemize}

\section{Education}\label{education}

\textbf{M.S. Finance, University of Illinois at Urbana-Champaign}
\hfill 2007

\begin{itemize}
\item
  Completed coursework in the graduate-level economics sequence,
  covering microeconomics, macroeconomics, and econometrics.
\item
  Conducted advanced research in finance, including research replication
  on large data sets like Compustat, using R and SAS. Modeled option
  valuation using binomial tree, Monte Carlo, and finite difference
  methods in C++.
\end{itemize}

\textbf{B.A. Mathematics and Computer Science, University of Illinois at
Urbana-Champaign} \hfill 2001

\begin{itemize}
\tightlist
\item
  Focused coursework in Probability, Statistics, Data Structures, Graph
  Theory, Numerical Methods, and Nonlinear Programming.
\end{itemize}

\section{Media Appearances and
Writings}\label{media-appearances-and-writings}

\subsection{Quotes and Media Mentions}\label{quotes-and-media-mentions}

\begin{itemize}
\tightlist
\item
  Highly experienced in media engagement, cited in over 300 articles and
  media references.
\item
  Top Outlets: \emph{New York Times} (32), \emph{Washington Post} (23),
  \emph{Vox} (21), \emph{Bloomberg} (10), \emph{Business Insider} (9),
  and more.
\end{itemize}

\subsection{Published Writing}\label{published-writing}

\begin{itemize}
\tightlist
\item
  Contributed articles to many publications, including but not limited
  to: \emph{The Nation} (19 articles), \emph{Dissent} (7), \emph{Vox}
  (6), \emph{Boston Review} (5), and the \emph{New York Times} (2).
\item
  Published the book \emph{Freedom From the Market} (New Press, 2021),
  highlighted as a ``Summer Book of 2021'' in the economics category by
  the \emph{Financial Times}. Reviews include: \emph{Democracy Journal},
  \emph{Foreign Policy}, \emph{Foreign Affairs}, \emph{Wall Street
  Journal}, and \emph{National Review}.
\item
  Co-authored \emph{Rewriting the Rules of the American Economy} (W.W.
  Norton, 2015), with Nobel laureate Joseph Stiglitz, summarizing the
  latest research in inequality.
\end{itemize}

\subsection{Media Appearances}\label{media-appearances}

\begin{itemize}
\tightlist
\item
  Garnered significant media presence with over 25 podcast appearances
  and 15 TV interviews, and amassed a following of over 50,000 on
  Twitter.
\item
  Notable Appearances: \emph{The Weeds} podcast (4 times), \emph{Planet
  Money} (3), \emph{Washington Journal} (2), \emph{CNBC} (2), \emph{CBS
  Sunday Morning}, and \emph{The Rachel Maddow Show}.
\end{itemize}

\emph{Full C.V. available upon request.}

\end{document}
